\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{slashed}
\usepackage{hyperref}

\title{Momentum-Space QCD Sum-Rule Setup for the $B_c(1P)$ Axial-Vector Mixing Angle}
\author{}
\date{}

\begin{document}

\maketitle

\section{Purpose and conventions}

We study the mixing between the two axial-vector $B_c(1P)$ basis states
associated with the ${}^3P_1$ and ${}^1P_1$ structures.  The current
implementation follows the Aliev et al. mixing-angle method, but the OPE is
evaluated in momentum space because both quark lines are heavy.

This note records the calculation implemented in
\texttt{BcMixingMomentum.wl}.  It is written so that every convention and
intermediate object can be checked independently before using the numerical
angle in a paper.

The quark content convention is
\begin{equation}
  B_c^+ = \bar b c .
\end{equation}

The two interpolating currents are taken as
\begin{align}
  J^A_\mu &= \bar b\,\gamma_\mu\gamma_5\,c,\\
  J^B_\mu &=
  i\,\bar b\,\sigma_{\mu\alpha}
  \frac{p^\alpha}{m_b+m_c}
  \gamma_5\,c,
\end{align}
where
\begin{equation}
  \sigma_{\mu\nu}=\frac{i}{2}[\gamma_\mu,\gamma_\nu].
\end{equation}
The explicit factor of $i$ in $J^B_\mu$ is retained.  This is important
because FeynCalc's \texttt{DiracSigma} already contains the conventional
$i/2$ commutator.

The factor $1/(m_b+m_c)$ is also essential.  Since
$[\bar Q Q]=3$ and $[p^\alpha]=1$, the unnormalized tensor current
$i\bar b\sigma_{\mu\alpha}p^\alpha\gamma_5c$ has mass dimension 4, while
$J^A_\mu$ has mass dimension 3.  The normalized current above makes both
currents dimension 3.

If the opposite flavor convention is used, for example $B_c^- = \bar c b$,
the sign of the quoted angle can change.  The absolute convention must
therefore be kept fixed when comparing to other papers.

\section{Mass-dimension check}

The quark field has dimension $3/2$, while $p^\alpha$, $m_b$, and $m_c$ have
dimension 1.  Therefore
\begin{equation}
  [J^A_\mu]=3,
  \qquad
  [J^B_\mu]=3
\end{equation}
only after the tensor current is normalized by $m_b+m_c$.

For currents with dimensions $d_i$ and $d_j$,
\begin{equation}
  [\Pi^{ij}_{\mu\nu}]
  =
  d_i+d_j-4,
\end{equation}
because of the $d^4x$ integration in the two-point function.  Thus the
normalized basis gives
\begin{equation}
  [\Pi^{AA}_1]=[\Pi^{AB}_1]=[\Pi^{BB}_1]=2.
\end{equation}
The spectral densities have the same mass dimension as the invariant
correlator,
\begin{equation}
  [\rho^{AA}]=[\rho^{AB}]=[\rho^{BB}]=2.
\end{equation}
In the present code the Borel moment is evaluated as
$\int ds\,e^{-s/M^2}\rho(s)$, so all three numerical moments carry one common
extra factor of $[ds]=2$.  This common convention does not affect the mixing
angle.

If the tensor current were left unnormalized, the dimensions would instead be
\begin{equation}
  [\rho^{AA}],\ [\rho^{AB}],\ [\rho^{BB}]
  =
  2,\ 3,\ 4,
\end{equation}
and the matrix entries in the angle formula would not be dimensionally
compatible.

\section{Implementation map}

The main code objects are:
\begin{itemize}
  \item \texttt{Correlator[channel, order]}:
  $\Pi_1^{ij}(p^2)$ after FeynCalc Dirac algebra and spin projection.
  \item \texttt{SpectralDensity[channel, ``pert'', s]}:
  $\rho_{\rm pert}^{ij}(s)$.
  \item \texttt{NumericBorelPi[channel, order, M2, s0]}:
  $\Pi^{ij}_{\rm order}(M^2,s_0)$.
  \item \texttt{NumericMixingAngleDegrees[M2, s0, ``total'']}:
  $\theta(M^2,s_0)$ from
  $\Pi_{\rm pert}^{ij}+\Pi_{G^2}^{ij}+\Pi_{G^3}^{ij}$.
\end{itemize}

The implemented OPE orders are
\begin{equation}
  \text{pert},\qquad G^2,\qquad \text{pertG2}=\text{pert}+G^2,
  \qquad G^3,\qquad \text{total}=\text{pert}+G^2+G^3.
\end{equation}
The implemented dimension-6 triple-gluon condensate
$\langle g_s^3G^3\rangle$ is the standard vacuum-averaged single-line
propagator term. Possible cross-line open-field $G^3$ terms need a separate
derivation.

\section{Correlators and spin-1 projection}

Define
\begin{equation}
  \Pi_{\mu\nu}^{ij}(p)
  =
  i\int d^4x\,e^{ip\cdot x}
  \langle 0 | T\{J^i_\mu(x)J^{j\dagger}_\nu(0)\}|0\rangle,
  \qquad i,j\in\{A,B\}.
\end{equation}

The invariant amplitude used for the axial-vector spin-1 state is extracted
with
\begin{equation}
  P^{\mu\nu}_{(1)}
  =
  \frac{1}{3}
  \left(
    g^{\mu\nu}
    -
    \frac{p^\mu p^\nu}{p^2}
  \right),
\end{equation}
so that
\begin{equation}
  \Pi_1^{ij}(p^2)=P^{\mu\nu}_{(1)}\Pi_{\mu\nu}^{ij}(p).
\end{equation}

The mixing angle is then obtained from
\begin{equation}
  \tan 2\theta
  =
  -\frac{2\Pi_1^{AB}}{\Pi_1^{AA}-\Pi_1^{BB}}.
\end{equation}
Numerically we use the quadrant-safe definition
\begin{equation}
  \theta_{\rm raw}
  =
  \frac{1}{2}
  \operatorname{atan2}
  \left(
    -2\Pi_1^{AB},
    \Pi_1^{AA}-\Pi_1^{BB}
  \right),
\end{equation}
and quote the principal branch
\begin{equation}
  \theta
  =
  \theta_{\rm raw}
  -
  \frac{\pi}{2}
  \operatorname{Round}
  \left(
    \frac{\theta_{\rm raw}}{\pi/2}
  \right),
  \qquad
  \theta\in[-45^\circ,45^\circ].
\end{equation}

\section{Momentum-space OPE}

The perturbative heavy-quark propagator is
\begin{equation}
  S_Q^{(0)}(k)
  =
  \frac{\slashed{k}+m_Q}{k^2-m_Q^2}.
\end{equation}

For the dimension-4 gluon condensate we use the background-field expansion
\begin{equation}
  S_Q(k)
  =
  S_Q^{(0)}(k)
  +
  g_sG_A^{\alpha\beta}T^A S_{Q,\alpha\beta}^{(G)}(k)
  +
  S_Q^{(G^2)}(k),
\end{equation}
where
\begin{align}
  S_{Q,\alpha\beta}^{(G)}(k)
  &=
  -\frac{1}{4}
  \frac{
    \sigma_{\alpha\beta}(\slashed{k}+m_Q)
    +
    (\slashed{k}+m_Q)\sigma_{\alpha\beta}
  }
  {(k^2-m_Q^2)^2},
  \\
  S_Q^{(G^2)}(k)
  &=
  \frac{\langle g_s^2G^2\rangle}{12}
  m_Q
  \frac{k^2+m_Q\slashed{k}}
  {(k^2-m_Q^2)^4}.
\end{align}
Equivalently,
\begin{equation}
  g_sG_A^{\alpha\beta}T^A S_{Q,\alpha\beta}^{(G)}(k)
  =
  -\frac{g_sG_A^{\alpha\beta}T^A}{4}
  \frac{
    \sigma_{\alpha\beta}(\slashed{k}+m_Q)
    +
    (\slashed{k}+m_Q)\sigma_{\alpha\beta}
  }
  {(k^2-m_Q^2)^2}.
\end{equation}
The one-gluon fields are contracted with
\begin{equation}
  \langle g_s^2G_A^{\alpha\beta}G_B^{\rho\sigma}\rangle
  =
  \frac{\delta_{AB}}{96}
  \langle g_s^2G^2\rangle
  \left(
    g^{\alpha\rho}g^{\beta\sigma}
    -
    g^{\alpha\sigma}g^{\beta\rho}
  \right),
\end{equation}
and
\begin{equation}
  \operatorname{Tr}(T^AT^B)=\frac{\delta^{AB}}{2}.
\end{equation}
Thus the color factor for the $S^{(G)}S^{(G)}$ piece is
\begin{equation}
  \frac{N_c^2-1}{192}\langle g_s^2G^2\rangle,
  \qquad N_c=3.
\end{equation}

The three projected OPE contributions are generated from
\begin{align}
  \Pi^{AA}_1 &\sim
  P^{\mu\nu}_{(1)}
  \operatorname{Tr}
  \left[
    \gamma_\mu\gamma_5
    S_c(k)
    \gamma_\nu\gamma_5
    S_b(k-p)
  \right],\\
  \Pi^{AB}_1 &\sim
  P^{\mu\nu}_{(1)}
  \operatorname{Tr}
  \left[
    \gamma_\mu\gamma_5
    S_c(k)
    i\sigma_{\nu\alpha}
    \frac{p^\alpha}{m_b+m_c}
    \gamma_5
    S_b(k-p)
  \right],\\
  \Pi^{BB}_1 &\sim
  P^{\mu\nu}_{(1)}
  \operatorname{Tr}
  \left[
    i\sigma_{\mu\alpha}
    \frac{p^\alpha}{m_b+m_c}
    \gamma_5
    S_c(k)
    i\sigma_{\nu\beta}
    \frac{p^\beta}{m_b+m_c}
    \gamma_5
    S_b(k-p)
  \right].
\end{align}

\section{Perturbative spectral densities}

For the perturbative loop, impose the two-particle cut
\begin{equation}
  k^2=m_c^2,\qquad (k-p)^2=m_b^2,
\end{equation}
which gives
\begin{equation}
  k\cdot p=\frac{s+m_c^2-m_b^2}{2},
  \qquad s=p^2.
\end{equation}

Define
\begin{equation}
  \lambda(s,m_b,m_c)
  =
  s^2+m_b^4+m_c^4
  -2sm_b^2-2sm_c^2-2m_b^2m_c^2 .
\end{equation}
The perturbative spectral densities are implemented as
\begin{equation}
  \rho_{\rm pert}^{ij}(s)
  =
  \frac{N_c}{16\pi^2}
  \frac{\sqrt{\lambda(s,m_b,m_c)}}{s}
  \frac{N^{ij}(s)}{(m_b+m_c)^{n_B^{ij}}},
\end{equation}
where $n_B^{AA}=0$, $n_B^{AB}=n_B^{BA}=1$, and $n_B^{BB}=2$ counts how many
tensor currents occur in the channel.  The unnormalized numerator functions
are
\begin{align}
  N^{AA}(s)
  &=
  -\frac{2}{s}
  \left[(m_b+m_c)^2-s\right]
  \left[(m_b-m_c)^2+2s\right],
  \\
  N^{AB}(s)
  &=
  6(m_b-m_c)\left[(m_b+m_c)^2-s\right],
  \\
  N^{BB}(s)
  &=
  2\left[
    -2(m_b^2-m_c^2)^2
    +(m_b^2-6m_bm_c+m_c^2)s
    +s^2
  \right].
\end{align}
Equivalently, after setting $N_c=3$,
\begin{align}
  \rho_{\rm pert}^{AA}(s)
  &=
  -\frac{3}{8\pi^2s^2}
  \left[(m_b+m_c)^2-s\right]
  \left[(m_b-m_c)^2+2s\right]
  \sqrt{\lambda(s,m_b,m_c)},\\
  \rho_{\rm pert}^{AB}(s)
  &=
  \frac{9}{8\pi^2s(m_b+m_c)}
  (m_b-m_c)
  \left[(m_b+m_c)^2-s\right]
  \sqrt{\lambda(s,m_b,m_c)},\\
  \rho_{\rm pert}^{BB}(s)
  &=
  \frac{3}{8\pi^2s(m_b+m_c)^2}
  \left[
    -2(m_b^2-m_c^2)^2
    +(m_b^2-6m_bm_c+m_c^2)s
    +s^2
  \right]
  \sqrt{\lambda(s,m_b,m_c)}.
\end{align}

The perturbative Borel moments are
\begin{equation}
  \Pi_{\rm pert}^{ij}(M^2,s_0)
  =
  \int_{(m_b+m_c)^2}^{s_0}
  ds\,
  e^{-s/M^2}
  \rho_{\rm pert}^{ij}(s).
\end{equation}

With this convention all three perturbative spectral densities have mass
dimension 2.  Without the factors of $(m_b+m_c)^{-n_B^{ij}}$, their
dimensions would be 2, 3, and 4 for $AA$, $AB$, and $BB$, respectively.

\section{Dimension-4 and dimension-6 gluon condensates}

The implemented condensate contribution is
\begin{equation}
  \Pi_{G^2}^{ij}
  =
  \Pi^{ij}[S_c^{(G^2)}S_b^{(0)}]
  +
  \Pi^{ij}[S_c^{(0)}S_b^{(G^2)}]
  +
  \Pi^{ij}[S_c^{(G)}S_b^{(G)}].
\end{equation}

After Feynman parametrization the terms have the schematic form
\begin{equation}
  \mathcal{A}_{G^2}^{ij}(x_1,x_2,s)
  =
  \sum_r
  C_r^{ij}(x_1,x_2,s)
  \left[
    m_c^2x_1^2
    +(m_b^2+m_c^2-s)x_1x_2
    +m_b^2x_2^2
  \right]^{-n_r}.
\end{equation}
The code then fixes the simplex by
\begin{equation}
  x_1=x,\qquad x_2=1-x.
\end{equation}
This gives
\begin{equation}
  \Delta(x,s)
  =
  m_c^2x+m_b^2(1-x)-s\,x(1-x).
\end{equation}

For the triple-gluon condensate we use the standard momentum-space
vacuum-averaged heavy-quark propagator term
\begin{equation}
  S_Q^{(G^3)}(k)
  =
  \frac{\langle g_s^3G^3\rangle}{48}
  \frac{
  (\slashed{k}+m_Q)
  \left[
    \slashed{k}(k^2-3m_Q^2)
    +2m_Q(2k^2-m_Q^2)
  \right]
  (\slashed{k}+m_Q)}
  {(k^2-m_Q^2)^6}.
\end{equation}
The implemented dimension-6 contribution is
\begin{equation}
  \Pi_{G^3}^{ij}
  =
  \Pi^{ij}[S_c^{(G^3)}S_b^{(0)}]
  +
  \Pi^{ij}[S_c^{(0)}S_b^{(G^3)}].
\end{equation}
This is the standard single-heavy-propagator contribution.  It does not yet
include any possible cross-line open-field terms of the schematic type
$S^{(G^2_{\rm open})}S^{(G)}$, which require an explicitly open two-gluon
propagator and a separate color/Lorentz derivation.

The $G^2$ and $G^3$ terms are not treated as ordinary smooth spectral
densities.  We instead use a direct Borel transform.  Set $s=-Q^2$ and write
\begin{equation}
  \Delta(x,-Q^2)
  =
  x(1-x)
  \left[Q^2+\bar s(x)\right],
\end{equation}
where
\begin{equation}
  \bar s(x)
  =
  \frac{m_c^2x+m_b^2(1-x)}{x(1-x)}.
\end{equation}

The Feynman-parameter amplitude is decomposed as
\begin{equation}
  -i\,\mathcal{A}_{G^r}^{ij}(x,-Q^2)
  =
  \sum_{\ell\geq 1}
  \frac{a_\ell^{ij}(x)}
  {\left[Q^2+\bar s(x)\right]^\ell}
  +
  \text{polynomial subtraction terms}.
\end{equation}
The polynomial subtraction terms vanish after the Borel transform.  The
working phase convention is the explicit factor $-i$ shown above.  This is a
bookkeeping convention for removing the loop-integration prefactor returned
by FeynCalc's Feynman-parameter amplitude.  This is the convention that
should be independently checked.

We use
\begin{equation}
  \mathcal{B}_{M^2}
  \left[
    \frac{1}{(Q^2+\bar s)^n}
  \right]
  =
  \frac{1}{(n-1)!\,(M^2)^{n-1}}
  e^{-\bar s/M^2}.
\end{equation}
Thus
\begin{equation}
  \Pi_{G^r}^{ij}(M^2,s_0)
  =
  \int_{x_-}^{x_+}
  dx\,
  e^{-\bar s(x)/M^2}
  \sum_{\ell\geq1}
  \frac{a_\ell^{ij}(x)}
  {(\ell-1)!\,(M^2)^{\ell-1}}.
\end{equation}

The continuum restriction is
\begin{equation}
  \bar s(x)\leq s_0,
\end{equation}
which gives
\begin{equation}
  x_\pm
  =
  \frac{
    s_0+m_b^2-m_c^2
    \pm
    \sqrt{\lambda(s_0,m_b,m_c)}
  }
  {2s_0}.
\end{equation}

\section{Total Borel moments and numerical test point}

The total moments used in the current numerical result are
\begin{equation}
  \Pi^{ij}(M^2,s_0)
  =
  \Pi_{\rm pert}^{ij}(M^2,s_0)
  +
  \Pi_{G^2}^{ij}(M^2,s_0)
  +
  \Pi_{G^3}^{ij}(M^2,s_0).
\end{equation}

The current default numerical inputs are
\begin{align}
  m_b &= 4.18~\text{GeV},\\
  m_c &= 1.27~\text{GeV},\\
  \langle g_s^2G^2\rangle &= 4\pi^2(0.012)~\text{GeV}^4,\\
  \langle g_s^3G^3\rangle &= 0.57~\text{GeV}^6,\\
  M^2 &= 10~\text{GeV}^2,\\
  s_0 &= 55~\text{GeV}^2.
\end{align}
For this point,
\begin{equation}
  x_- = 0.3322728664,\qquad
  x_+ = 0.9560816791.
\end{equation}

The perturbative moments are
\begin{align}
  \Pi_{\rm pert}^{AA} &= 0.1441716826,\\
  \Pi_{\rm pert}^{AB} &= -0.1051577192,\\
  \Pi_{\rm pert}^{BB} &= 0.1348134513.
\end{align}
The gluon-condensate moments are
\begin{align}
  \Pi_{G^2}^{AA} &= -0.0003658277,\\
  \Pi_{G^2}^{AB} &= 0.0002309420,\\
  \Pi_{G^2}^{BB} &= -0.0001888869.
\end{align}
The triple-gluon-condensate moments are
\begin{align}
  \Pi_{G^3}^{AA} &= 0.0000700979,\\
  \Pi_{G^3}^{AB} &= -0.0000493659,\\
  \Pi_{G^3}^{BB} &= 0.0000310238.
\end{align}
Thus
\begin{align}
  \Pi_{\rm total}^{AA} &= 0.1438759528,\\
  \Pi_{\rm total}^{AB} &= -0.1049761432,\\
  \Pi_{\rm total}^{BB} &= 0.1346555882.
\end{align}

The corresponding angles are
\begin{align}
  \theta_{\rm pert} &= 43.726118943^\circ,\\
  \theta_{\rm pert+G^2} &= 43.747426660^\circ,\\
  \theta_{\rm pert+G^2+G^3} &= 43.742693524^\circ.
\end{align}
At this point the relative condensate corrections are
\begin{align}
  \frac{\Pi_{G^2}^{AA}}{\Pi_{\rm pert}^{AA}} &= -0.002537,\\
  \frac{\Pi_{G^2}^{AB}}{\Pi_{\rm pert}^{AB}} &= -0.002196,\\
  \frac{\Pi_{G^2}^{BB}}{\Pi_{\rm pert}^{BB}} &= -0.001401,\\
  \frac{\Pi_{G^3}^{AA}}{\Pi_{\rm pert}^{AA}} &= 0.000486,\\
  \frac{\Pi_{G^3}^{AB}}{\Pi_{\rm pert}^{AB}} &= 0.000469,\\
  \frac{\Pi_{G^3}^{BB}}{\Pi_{\rm pert}^{BB}} &= 0.000230.
\end{align}

\section{How to reproduce the numerical check}

In Mathematica, load the implementation with
\begin{verbatim}
SetDirectory["/Users/sbilmis/Bc_mixing"];
Get["BcMixingMomentum.wl"];
\end{verbatim}
Then evaluate
\begin{verbatim}
NumericOPESummary[10, 55]
NumericMixingAngleDegrees[10, 55, "pert"]
NumericMixingAngleDegrees[10, 55, "pertG2"]
NumericMixingAngleDegrees[10, 55, "total"]
MixingMassDimensionReport[]
CheckMixingMassDimensions[]
PerturbativeSpectralDensityDimensionReport[]
\end{verbatim}
For window studies one can scan
\begin{verbatim}
MixingAngleTable[{8, 12, 1}, {50, 60, 5}, "total"]
OPEConvergenceDataset[{8, 12, 1}, {50, 60, 5}]
\end{verbatim}

\section{Checklist for independent verification}

A theorist can check the calculation in the following order:
\begin{enumerate}
  \item Confirm the current convention, especially the explicit factor of
  $i$ in $J^B_\mu$, the normalization $p^\alpha/(m_b+m_c)$, and the
  definition of $\sigma_{\mu\nu}$.
  \item Reproduce the three projected perturbative traces and verify the
  numerator functions $N^{AA}(s)$, $N^{AB}(s)$, and $N^{BB}(s)$.
  \item Check the two-body phase-space normalization
  $N_c\sqrt{\lambda}/(16\pi^2s)$ used in $\rho_{\rm pert}^{ij}(s)$.
  \item Verify the background-field propagator terms and the color factor in
  the $S^{(G)}S^{(G)}$ contribution.
  \item Independently derive the direct Borel formula for the $G^2$ and $G^3$
  terms, including the $-i$ phase convention.
  \item Check whether the standard single-line $G^3$ propagator contribution
  is sufficient, or whether cross-line open-field $G^3$ terms must be added.
  \item Check that $\Pi_{G^2}/\Pi_{\rm pert}$ and
  $\Pi_{G^3}/\Pi_{\rm pert}$ remain small in the accepted Borel window.
  \item Determine the final working window using OPE convergence, Borel
  stability, and pole-dominance criteria.
\end{enumerate}

\end{document}
